---
title: "PIC 10C Final Project Sandbox 2"
output: md_document
---

## Initial creation of package

In R:
library(Rcpp)
Rcpp.package.skeleton("Anton1")  

In the console:
R CMD build Anton1  
R CMD check Anton1  
^ that is all in the terminal

Back in R:
compileAttributes("/Users/Anton/PIC-10C-Final-Project/Anton1/", verbose=TRUE)

library(tools)  
package_native_routine_registration_skeleton("/Users/Anton/PIC-10C-Final-Project/Anton1/", character_only = FALSE)
^ copy the output of this into the file ~/Anton1/src/init.c

install.packages("~/PIC-10C-Final-Project/Anton1_1.0.tar.gz", repos = NULL, type = "source")


```{r}
library(Anton1)

rcpp_hello_world()
```

## Adding a function to convert a number to celsius, sum a vector, and find the mean of a vector
```{r}
to_celsius(10)

to_celsius(100.0)
```

```{r}
cosa1 <- 1:10

sumCpp(cosa1)
sumCpp(15:10)

meanC(cosa1)
meanC(15:10)
```

```{r}
paste2("hi", "bye")

removePunct("_-#h3/l/l0!-_")
removePunct2("_-#h3/l/l0!-_")

cosa2 <- c("hi.....$poiajefa;'a'", "hello", "this-is_a#Cosa", "'I /./.,/dont*%$#% know@##@$}{ how|| to?><-=+_ type'")

stuff <- removePunct2(cosa2)
stuff
```

```{r}
load(url("http://www.stat.ucla.edu/~vlew/SP18stat20/bb102.RData"))
salaries <- bb102[["salaries10.2"]]

salaries_long <- c(salaries$Salary, salaries$Salary, salaries$Salary, salaries$Salary,salaries$Salary, salaries$Salary, salaries$Salary)

head(salaries$Salary, 10)
head(removePunct2(salaries$Salary), 10)
head(gsub("\\$|,", "", salaries$Salary), 10)

system.time(removePunct2(salaries$Salary))
system.time(gsub("\\$|,", "", salaries$Salary))

system.time(removePunct2(salaries_long))
system.time(gsub("\\$|,", "", salaries_long))
```











