---
title: "PIC 10C Final Project Sandbox 2"
output: md_document
---

## Initial creation of package

In R:
library(Rcpp)
Rcpp.package.skeleton("Anton1")  

In the console:
R CMD build Anton1  
R CMD check Anton1  
^ that is all in the terminal

Back in R:
compileAttributes("/Users/Anton/PIC-10C-Final-Project/Anton1/", verbose=TRUE)

library(tools)  
package_native_routine_registration_skeleton("/Users/Anton/PIC-10C-Final-Project/Anton1/", character_only = FALSE)
^ copy the output of this into the file ~/Anton1/src/init.c

install.packages("~/PIC-10C-Final-Project/Anton1_1.0.tar.gz", repos = NULL, type = "source")


```{r}
library(Anton1)

rcpp_hello_world()
```

## Adding a function to convert a number to celsius, sum a vector, and find the mean of a vector
```{r}
cosa1 <- 1:10

to_celsius(100.0)

sumCpp(cosa1)

meanC(cosa1)

to_celsius(10)

paste2(c("hi"), c("bye"))

cosa2 <- c("hi.....$poiajefa;'a'", "hello", "this-is_a#Cosa")

stuff <- removePunct2(cosa2)
stuff

removePunct2("I /./.,/dont*%$#% know@##@$}{ how|| to?><-=+_ type")
```











